---
title: "Companies House"
author: "Barry Bullas"
date: "16/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

list_of_packages <- c("rvest", "dplyr", "httr", "xml2", "jsonlite", "DT", "here", "readtext", "secret")

new_packages <- list_of_packages[!(list_of_packages %in% installed.packages()[,"Package"])]
if(length(new_packages)) install.packages(new_packages, repos = "https://cloud.r-project.org/")

#Load required packages
lapply(list_of_packages, library, character.only = TRUE)
```

## AIM

This project explores how to retrieve data from the [Companies House API](https://developer.companieshouse.gov.uk/api/docs/).

## Set up a Companies House account
To be able to explore and perform tests with the Companies House API, you need to register a [user account](https://developer.companieshouse.gov.uk/developer/signin) with Companies House, and then generate an [API key](https://developer.companieshouse.gov.uk/api/docs/index/gettingStarted/apikey_authorisation.html) for use in each API request.  You also need to provide the IP address that you will be requesting from (remember to update it if you get any 403 errors).

```{r }
# API KEY
# I store my api keys using the secret package so they are encrypted and can only be accessed by me
# You can replace the next line of code with the line below if you don't use the Secret package
# my_key <- 'enter your api key'

my_key <- get_secret("Companies_House_API_KEY", key = local_key() , vault = here())

# Static URL 
static_url <- 'https://api.companieshouse.gov.uk/'

# urls for functions
search_all_url <- paste0(static_url, 'search')
search_companies_url <- paste0(static_url, 'search/companies')
search_officer_url <- paste0(static_url, 'search/officers')
search_disq_officer_url <- paste0(static_url, 'search/disqualified-officers')

# query to search for
ch_query <- 'Harley Davidson'

query_list <- list(q = ch_query)

# Get the authorities by passing the GET commmand the URL and the user text
get_response <- GET(search_companies_url,  query = query_list, authenticate(my_key, ''))

#Check status of response (
if (status_code(get_response)==200)
  {
  # 200 = sucessful
  
  # Check http_type() of the response
  http_type(get_response)
  
  #list the headers
  headers(get_response)
  
  # Parse returned text with fromJSON()
  search_content <- fromJSON(content(get_response, as = "text",  encoding = "UTF-8"), simplifyDataFrame = TRUE)
  
  #The data should be in a list
  typeof(search_content)
  
  # The companies are contained within the items section of the json
  companies_returned <- search_content[["items"]]
  
  # Keep the key columns that we need
  companies_returned <- subset(companies_returned, select = c(company_number, title, date_of_creation, date_of_cessation, address_snippet) )
  
  #Display the data in a datatable
  datatable(head(companies_returned, 10))
  
} else if (status_code(get_response)==429)
{
  # Rate limit reached
  # limit is currently 600 requests in 5 minutes - wait before tyring again
  
}else if (status_code(get_response)==403)
{
  # Access Forbidden
  # May be caused by api key being incorect or the ip address has not been added to companies house account

  }
```
